Untitled

### 2024-10-21 analysis/initial_conditions/initial_conditions.qmd
More IC

---
title: "Untitled"
format: revealjs
---

```{r setup}
library(lubridate)
library(ggplot2)
library(data.table)
library(metR)
library(rcdo)

@@

1. Use initial conditions from a very average day/month.
2. Run experiments with changing sea ice initial condtions: 
  1. Experiments with high initial sea ice
  2. Experiments with low sea ice.

@@

1. Compute an error metric between dates and the climatology and chose the lowest. 
2. Three posible metrics:
  1. RMSE 
  2. IIEE
  3. Extent difference (IIEE, is better overall because it also includes location error, so I discard this)

---

@@

---

@@

---

```{r}
min_error_data |> 
  _[variable == "iiee"] |> 
  _[, label := paste0(formatC(month(time), width = "2", flag = "0"), " - ", as.character(time))] |> 
  s2_climatology[i = _, on = .NATURAL] |> 
  ggplot(aes(xgrid, ygrid)) +
  geom_contour_fill(aes(z = aice - clim, fill = after_stat(level))) +
  geom_contour2(aes(z = aice), breaks = 0.15) +
  geom_contour2(aes(z = clim), breaks = 0.15, linetype = 2) +
  scale_fill_divergent_discretised() +
  geomcoord_antarctica +
  geom_antarctica_path +
  facet_wrap(~ label) +
  wide_legend +
  labs(title = "iiee")
```

---

```{r}
min_error_data |> 
  _[variable == "rmse"] |> 
  _[, label := paste0(formatC(month(time), width = "2", flag = "0"), " - ", as.character(time))] |> 
  s2_climatology[i = _, on = .NATURAL] |> 
  ggplot(aes(xgrid, ygrid)) +
  geom_contour_fill(aes(z = aice - clim, fill = after_stat(level))) +
  geom_contour2(aes(z = aice), breaks = 0.15) +
  geom_contour2(aes(z = clim), breaks = 0.15, linetype = 2) +
  scale_fill_divergent_discretised() +
  geomcoord_antarctica +
  geom_antarctica_path +
  facet_wrap(~ label) +
  wide_legend +
  labs(title = "rmse")
```

>>>>

---
title: "Untitled"
format: revealjs
execute:
  cache: true
---

```{r setup}
#| cache: false
library(lubridate)
library(ggplot2)
library(data.table)
library(metR)
library(rcdo)

@@

1.  Use initial conditions from a very average day/month.
2.  Run experiments with changing sea ice initial condtions:
3.  Experiments with high initial sea ice
4.  Experiments with low sea ice.

@@

1.  Compute an error metric between dates and the climatology and chose the lowest.
2.  Three possible metrics:
    1.  RMSE
    2.  IIEE
    3.  Extent difference (IIEE, is better overall because it also includes location error, so I discard this)

------------------------------------------------------------------------

@@

------------------------------------------------------------------------

@@

------------------------------------------------------------------------
```{r}
breaks <- seq(-0.9, 0.9, by = 0.1)
```
```{r}
min_error_data |> 
  _[variable == "iiee"] |> 
  _[, label := paste0(formatC(month(time), width = "2", flag = "0"), " - ", as.character(as.Date(time)))] |> 
  s2_climatology[i = _, on = .NATURAL] |> 
  ggplot(aes(xgrid, ygrid)) +
  geom_contour_fill(aes(z = aice - clim, fill = after_stat(level)), breaks = breaks) +
  geom_contour2(aes(z = aice), breaks = 0.15) +
  geom_contour2(aes(z = clim), breaks = 0.15, linetype = 2) +
  scale_fill_divergent_discretised() +
  geomcoord_antarctica +
  geom_antarctica_path +
  facet_wrap(~ label, ncol = 6) +
  wide_legend +
  labs(title = "iiee")
```

------------------------------------------------------------------------

```{r}
min_error_data |> 
  _[variable == "rmse"] |> 
  _[, label := paste0(formatC(month(time), width = "2", flag = "0"), " - ", as.character(as.Date(time)))] |> 
  s2_climatology[i = _, on = .NATURAL] |> 
  ggplot(aes(xgrid, ygrid)) +
  geom_contour_fill(aes(z = aice - clim, fill = after_stat(level)), breaks = breaks) +
  geom_contour2(aes(z = aice), breaks = 0.15) +
  geom_contour2(aes(z = clim), breaks = 0.15, linetype = 2) +
  scale_fill_divergent_discretised() +
  geomcoord_antarctica +
  geom_antarctica_path +
  facet_wrap(~ label, ncol = 6) +
  wide_legend +
  labs(title = "rmse")
```
